One more attempt on ArXe

### 2016-05-27 theo_results.tex
correct Uwes statements about the theoretical structures

\section{Theoretical Results
\label{sec:th_results}}
%
%
\begin{table}[h]
\small
\centering
\caption{Structural and calculated properties of some model clusters.
The cluster structures are characterized by the number of Ar and Xe atoms, and are arranged in three groups according to gross structural properties. 
The first group contains Xe core-Ar shell systems of various size and relative Xe content.
In the second group, model structures for small clusters are displayed, in which 1-2 Xe atoms are added at systematically varied locations to an icosahedric Ar clusters consisting of one or two full shells, or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms, while keeping the geometry of the original Xe lattice.
The last group contains data for calculated minimal energy structures of mixed ArXe clusters.\protect\cite{marques}
The columns `ICD' and `ETMD' are the respective partial decay widths in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in the total decay width.
See text for details.
\label{table:theo_gammas}
}
\begin{tabular}{rrrrcccccrrr}
\toprule
\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
\midrule
 1 &     1 &    12 &  7.7  & cl    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
 2 &     1 &    54 &  1.8  & cl    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
 3 &     2 &    53 &  3.6  & cl    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
 4 &  1415 &   642 & 68.8  & cl    &         &          & 7.039 & 2.573 &  73.2& suppl.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
 5 &   561 &  3310 & 14.5  & cl    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5

@@

 6 &     1 &    13 &  7.1  & cl    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
 7 &     1 &    13 &  7.1  & cl    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
 8 &     1 &    13 &  7.1  & cl    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
 9 &     2 &    13 & 13.3  & cl    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
10 &     2 &    13 & 13.3  & cl    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
11 &     2 &    13 & 13.3  & cl    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
12 &     1 &    55 &  1.8  & cl    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
13 &     1 &    55 &  1.8  & cl    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
14 &     1 &    55 &  1.8  & cl    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     

@@

20 &     2 &    36 &  5.3  & cl    &         &          & 0.117 & 0.151 &  43.6& suppl.\\                        % Ar$_{36}$Xe$_{2}$   

>>>>

\section{Theoretical Results
\label{sec:th_results}}
%
%
\begin{table}[h]
\small
\centering
\caption{Structural and calculated properties of some model clusters.
The cluster structures are characterized by the number of Ar and Xe atoms,
and are arranged in three groups according to gross structural properties. 
The first group contains Xe core-Ar shell systems of various
size and relative Xe content.
In the second group, model structures for small clusters are displayed,
in which 1-2 Xe atoms are added at systematically varied locations
to an icosahedric Ar clusters consisting of one or two full shells,
or in which 1-6 Ar atoms of such cluster were replaced by Xe atoms.
Afterwards the cluster structures were optimized using force fields to
give local minimum structures.
The last group contains data for calculated minimal energy structures
of mixed ArXe clusters.\protect\cite{marques}
The cluster structures are classified into core-shell structures (cs),
structures with seggregated xenon atoms (in) and completely mixed
structures.
The columns `ICD' and `ETMD' are the respective partial decay widths
in \unit[$10^{-4}$]{eV}, and `\% ICD' gives the percentage of ICD in
the total decay width.
See text for details.
\label{table:theo_gammas}
}
\begin{tabular}{rrrrcccccrrr}
\toprule
\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD & Fig.\\ %$\Gamma_{\rm ICD,ETMD}$\\
\midrule
 1 &     1 &    12 &  7.7  & cs    &         &          & 0.000 & 0.000 &  -- &\\ %    0.0            \\     ArXe\_2\_1atom      
 2 &     1 &    54 &  1.8  & cs    &         &          & 0.000 & 0.000 &  -- & \ref{figure:xe_3_in}\\ %    0.0            \\     ArXe\_3\_1atom      
 3 &     2 &    53 &  3.6  & cs    &         &          & 0.033 & 0.167 &  16.7& \ref{figure:xe_3_in}\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
 4 &  1415 &   642 & 68.8  & cs    &         &          & 7.039 & 2.573 &  73.2& suppl.\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     
 5 &   561 &  3310 & 14.5  & cs    &         &          &       &       &  85  & \ref{figure:xe_6_lay5}\\ % c6l5

@@

 6 &     1 &    13 &  7.1  & cs    & surface &          & 0.792 & 0.000 & 100.0& \ref{figure:surf}\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
 7 &     1 &    13 &  7.1  & cs    & edge    &          & 0.013 & 0.000 & 100.0&\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
 8 &     1 &    13 &  7.1  & cs    & vertex  &          & 0.050 & 0.000 & 100.0&\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
 9 &     2 &    13 & 13.3  & cs    &         & closest  & 0.101 & 0.151 &  40.1& \ref{figure:2tops}\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
10 &     2 &    13 & 13.3  & cs    &         & middle   & 0.159 & 0.008 &  95.4& \ref{figure:2tops}\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
11 &     2 &    13 & 13.3  & cs    &         & furthest & 0.159 & 0.002 &  98.9& \ref{figure:2tops}\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
12 &     1 &    55 &  1.8  & cs    & surface &          & 0.064 & 0.000 & 100.0& \ref{figure:surf}\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
13 &     1 &    55 &  1.8  & cs    & edge    &          & 0.048 & 0.000 & 100.0&\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
14 &     1 &    55 &  1.8  & cs    & vertex  &          & 0.027 & 0.000 & 100.0&\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     

@@

20 &     2 &    36 &  5.3  & cs    &         &          & 0.117 & 0.151 &  43.6& suppl.\\                        % Ar$_{36}$Xe$_{2}$   
